\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-07 chapters/patients_table.tex
funding

\begin{tabular}{llllllllr}
  \toprule
  \textbf{ID}  & \textbf{Age} & \textbf{Sex} & \textbf{Hand.} &
  \textbf{Diagnosis}
  & \textbf{Speech}     & \textbf{Trach.} & \textbf{Communication}          &
  \textbf{Cls.} \\ \midrule
  PA1 & 58  & M   & L     & bulbar-onset \acs{als} & anarthric  & no          & tablet                 & 3  \\
  PB1 & 41  & M   & L     & \acs{fa} & dysarthric & no          & verbal                 & 3  \\
  PB2 & 43  & F   & R     & \acs{fa} & dysarthric & no          & verbal                 & 3  \\
  PB4 & 48  & M   & R     & \acs{fa} & dysarthric & no          & verbal                 & 3  \\
  PC2 & 43  & M   & R     & brainstem stroke & anarthric  & yes         & \makecell[l]{prompting\\+eye movement} & 2 \\
  PC3 & 43  & F   & R     & brainstem stroke & anarthric  & yes         & letterboard            & 2 \\
  PC4 & 54  & M   & R     & \makecell[l]{left cerebellar stroke \\ (trombosis of the basilar artery)} & anarthric  & yes & letterboard & 2 \\
  \bottomrule
\end{tabular}

>>>>

\begin{tabular}{llllllllrr}
  \toprule
  \textbf{ID}  & \textbf{Age} & \textbf{Sex} & \textbf{Hand.} &
  \textbf{Diagnosis} & \textbf{Speech} & \textbf{Trach.} & \textbf{Communication} &
  \textbf{Cls. W} & \textbf{Cls. KB} \\ \midrule
  PA1 & 58  & M   & L     & bulbar-onset \acs{als} & anarthric  & no          & tablet                 & 3  & 4 \\
  PB1 & 41  & M   & L     & \acs{fa} & dysarthric & no          & verbal                 & 3  & 3 \\
  PB2 & 43  & F   & R     & \acs{fa} & dysarthric & no          & verbal                 & 3  & 3 \\
  PB4 & 48  & M   & R     & \acs{fa} & dysarthric & no          & verbal                 & 3  & 3 \\
  PC2 & 43  & M   & R     & brainstem stroke & anarthric  & yes         &  \makecell[l]{prompting\\+eye movement} & 2 & 4  \\
  PC3 & 43  & F   & R     & brainstem stroke & anarthric  & yes         & letterboard            & 2 & 3 \\
  PC4 & 54  & M   & R     & \makecell[l]{left cerebellar stroke \\ (trombosis of the basilar artery)} & anarthric  & yes & letterboard & 2 & 3 \\
  \bottomrule
\end{tabular}

### 2024-10-07 chapters/stbf_struct.tex
Update bttda formulation
cover page
funding

\newcommand{\pv}[1]{
	%\ifdim#1pt<0.05pt
	%	\cellcolor{black!20}
	%\fi
	%\ifdim#1pt<0.001pt
	%	$< 0.001$
	%\else
	%	\ifdim#1pt=1.000pt
	%		\multicolumn{1}{c}{--}
	%	\else
	%		$#1$
	%	\fi
	%\fi
	#1
}
% Kronecker-structured LDA ====================================================

  \emph{This chapter, except section~\ref{sec:stbf-struct-kronlda}, was
  published by~\textcite{VanDenKerchove2022}}.

@@

  \begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/accuracy.eps}
    \caption[Clasifier accuracy in function of available training data.]{%
      Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\autoref{fig:accuracy_ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}
	\begin{table}[h]
		\centering
		\input{chapters/stbf_struct_tests_1.tex}
    \caption[Statistical significance of differences in classifier performance (1 repetition).]{%
      Statistical significance of differences in classifier performance.
      $p$-values calculated by one-sided paired Wilcoxon rank-sum test with
			Holm correction using one testing trial for different classifiers
			and levels of data availability. $p$-values $<0.05$ are considered significant
			and marked in grey.}
		\label{tab:p_values_1}

		\centering
		\input{chapters/stbf_struct_tests_2.tex}
		\caption[Statistical significance of differences in classifier performance (2 repetitions).]{%
      $p$-values as in \autoref{tab:p_values_1} averaging over two testing trials.}
		\label{tab:p_values_2}

		\centering
		\input{chapters/stbf_struct_tests_3.tex}
    \caption[Statistical significance of differences in classifier performance (5 repetitions).]{%
      $p$-values as in \autoref{tab:p_values_1} averaging over five testing trials.}
		\label{tab:p_values_5}
	\end{table}
	\unskip

@@

	\begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/training_time.eps}
    \caption[Classifier training time.]{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			x\textsc{dawn+rg}.}
		\label{fig:training_time}
	\end{figure}

@@

  \subsection{Extension to \ac{lda}}
  \label{sec:stbf-struct-kronlda}
  \todo{cite proof (or reiterate)}

@@

\todo{
in conclusion: LCMV struct might be to restrictive
Toeplitzlda MEG paper}

\todo{in conclusion: extension to the TFR domain}
%\begin{equation}
%	\mat{C} = \mat{S}\otimes\mat{T}
%\end{equation}
%Tapering, Toeplitz and shrinkage
%\subsection{The Kronecker sum covariance model}
%\begin{equation}
%	\mat{C} = \sum_k^{CS}\mat{S}\otimes\mat{T}
%\end{equation}

>>>>

\chapter{Kronecker-structured linear decoding}
\label{sec:stbf-struct}
\newcommand{\pv}[1]{
	%\ifdim#1pt<0.05pt
	%	\cellcolor{black!20}
	%\fi
	%\ifdim#1pt<0.001pt
	%	$< 0.001$
	%\else
	%	\ifdim#1pt=1.000pt
	%		\multicolumn{1}{c}{--}
	%	\else
	%		$#1$
	%	\fi
	%\fi
	#1
}
% Kronecker-structured LDA ====================================================

  \emph{This chapter, except section~\ref{sec:stbf-struct-kronlda}, was
  published as~\textcite{VanDenKerchove2022}}.

@@

  \begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/accuracy.eps}
    \caption[Clasifier accuracy in function of available training data.]{%
      Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\autoref{fig:accuracy_ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}
  \begin{table}[p]
		\centering
    \makebox[\textwidth][c]{%
		\input{chapters/stbf_struct_tests_1.tex}
  }
    \caption[Statistical significance of differences in classifier performance (1 repetition).]{%
      Statistical significance of differences in classifier performance.
      $p$-values calculated by one-sided paired Wilcoxon rank-sum test with
			Holm correction using one testing trial for different classifiers
			and levels of data availability. $p$-values $<0.05$ are considered significant
			and marked in grey.}
		\label{tab:p_values_1}
    \bigskip

		\centering
    \makebox[\textwidth][c]{%
		\input{chapters/stbf_struct_tests_2.tex}
    }
		\caption[Statistical significance of differences in classifier performance (2 repetitions).]{%
      $p$-values as in \autoref{tab:p_values_1} averaging over two testing trials.}
		\label{tab:p_values_2}
    \bigskip

		\centering
    \makebox[\textwidth][c]{%
		\input{chapters/stbf_struct_tests_3.tex}
    }
    \caption[Statistical significance of differences in classifier performance (5 repetitions).]{%
      $p$-values as in \autoref{tab:p_values_1} averaging over five testing trials.}
		\label{tab:p_values_5}
	\end{table}
	\unskip

@@

	\begin{figure}
		\includegraphics[width=.66\linewidth]{figures/stbf_struct/training_time.eps}
    \caption[Classifier training time.]{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			x\textsc{dawn+rg}.}
		\label{fig:training_time}
	\end{figure}

@@

@@

%\begin{equation}
%	\mat{C} = \mat{S}\otimes\mat{T}
%\end{equation}
%Tapering, Toeplitz and shrinkage
%\subsection{The Kronecker sum covariance model}
%\begin{equation}
%	\mat{C} = \sum_k^{CS}\mat{S}\otimes\mat{T}
%\end{equation}
